---
  title: "R Data Types and Data Structures"
output:
  html_document:
  df_print: paged
editor_options:
  chunk_output_type: console
---

```{r}
dfPatients= read.csv('Data/emergency.csv')
```

## way to chect the data type

```{r}
str(dfPatients)
```

```{r}
dfPatients

```

```{r}
str(dfPatients$Condition)

```

## Different way to access

```{r}
dfPatients$Condition
str(dfPatients$Condition)
```

```{r}
dfPatients[['Condition']]
str(dfPatients[['Condition']])
```

```{r}
dfPatients['Condition']
str(dfPatients['Condition'])
```

```{r}
dfPatients[,'Condition']
str(dfPatients[,'Condition'])
```

```{r}
dfPatients[2]
str(dfPatients[2])
```

##How to acces and chech value of column

```{r}
dfPatients[2]=='serious'

```

```{r}
dfPatients[dfPatients[2]=='serious'] ## Shows only the secfied value of that coloum
```

```{r}
dfPatients[dfPatients[2]=='serious',]## Shows all colums where they are specfied value

```

## 

```{r}
sum(dfPatients$Condition=='serious')
```

```{r}
mean(dfPatients$Condition=='serious')
```

```{r}
median(dfPatients$Condition=='serious')
```

```{r}
dfPatients$Insurance
```

```{r}
mode(dfPatients$Condition=='serious')
```

###My own experiment \# `{r} #  # serious_p=mean(dfPatients$Condition=='serious') # fair_p=mean(dfPatients$Condition=='fair') # good_p=mean(dfPatients$Condition=='good') # p=c(serious_p,fair_p,good_p) # print(p) #` \# `{r} # serious_p=mean(dfPatients$Insurance=='insured') # fair_p=mean(dfPatients$Insurance=='not insured') #  # p=c(serious_p,fair_p) # print(p) #  #` \# \# `{r} #  # s=c(1,0) # print(s) #` \# `{r} #  # aaaaa=sample(s, size = 100, replace = TRUE, prob = p) # sum(aaaaa) #  #`

## 

```{r}
dfPatients$Condition=factor(dfPatients$Condition)
```

```{r}
# not so good methord to change since all values get changed
read.csv("Data/emergency.csv",row.names=1,stringsAsFactors = TRUE)
```

#Types of Catagorical vales \## Binary \## Multivalue \## Ordinal

# Best way to do it

```{r}

dfPatients=read.csv("Data/emergency.csv",row.names=1)
```

```{r}
contineous_features=c()
catagorical_col=c('Condition','Insurance')
```

```{r}
dfPatients[,catagorical_col] = lapply(dfPatients[,catagorical_col] , factor)
str(dfPatients)
```

```{r}

str(dfPatients)
```

```{r}
# c('serious','insured')
sum(dfPatients[dfPatients$Condition=='serious',]$Insurance=='insured')
```

```{r}
mean(dfPatients[dfPatients$Condition=='serious',]$Insurance=='insured')

```

## Logacal operator in R

```{r}
vec1=c(TRUE,FALSE,TRUE,TRUE,FALSE,TRUE)
vec2=c(FALSE,TRUE)
vec2&vec1
```
## the operation & is performed to do intersection
```{r}

mean(dfPatients$Condition=='serious' & dfPatients$Insurance=='insured')

```
##defrving formula for conditional probablity
```{r}
mean(dfPatients$Condition=='serious' & dfPatients$Insurance=='insured')/mean(dfPatients$Insurance=='insured')
```
####it is simlar to
```{r}

mean(dfPatients[dfPatients$Insurance=='insured',]$Condition=='serious')
```


