---
title: "bur_ridership"
author: '''Chaitanya Sachidanand'',''Sudhanva HG'',''Dhruva Nayak'''
date: "2023-08-29"
output: pdf_document
editor_options:
  chunk_output_type: console
html_document:
  df_print: paged
---

# 1. Consider the following model for a bus-ridership analysis: ### at
each stop, each passenger is likely to get off the bus independent of
others with a 20% chance; 

## at every stop, there is a 50%/40%/10% chance of 0/1/2 passengers getting on board; 

## the bus never gets full; new passengers at any stop can always be accommodated;

## bus is empty when it arrives at the first stop. 

Write an R code to calculate using simulation the probability that the bus is empty after visiting the tenth stop.


### Code to simulate entering and exiting the bus by useing sample and probablity

```{r}
entering_bus = function(){
  
  return(sample(c(0,1,2),size = 1,prob = c(0.50,0.40,0.10)))
}
exiting_bus = function(){
  return(sample(c(1,0),size = 1,prob = c(0.20,0.80)))
}

```

### Code to test the function

```{r}
entering_bus()
exiting_bus()
```

### code to simulate the exinting and entring the bus till 10 stops

```{r}
bus_10Passenger = function(){
  bus_seat=c()
  for (j in c(1:10)) {
    if (j == 1) {
      # c(x, "b")
      bus_seat=c(bus_seat,entering_bus())
    }
    else if(bus_seat[j-1]==0){
    bus_seat=c(bus_seat,entering_bus())
    }
    else {
    bus_seat=c(bus_seat,bus_seat[j-1]+entering_bus()-exiting_bus())
    # bus_seat
    }
  }
  return(bus_seat)
}

```

running 100000 simulation people entering and exiting the bus

```{r}
nsimuationss=100000
simulatedData = replicate(nsimuationss,bus_10Passenger())
```

count of no entries present in the 10th stop

```{r}
table(simulatedData[10,])
```

probablity that the bus is empty at 10th stop

```{r}
sum(simulatedData[10,]==0)/length(simulatedData[10,])
```
